---
title: "Google Analytics"
author: "Christine Iyer"
date: "October 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}

library(googleAnalyticsR)
```


## Google Analytics

### Step 1
Authorize API

```{r auth and account}
ga_auth()

my_accounts <- ga_account_list()
View(my_accounts)
ga_id <- 63145830
```


```{r}
# start_date <- "2020-01-21"
# end_date <-  "2020-01-28"
# 
# campaign_filter <- dim_filter(dimension="region",operator="EXACT",expressions="Connecticut")
# my_filter_clause <- filter_clause_ga4(list(campaign_filter))
# 
# GALast <- google_analytics(ga_id, date_range = c(start_date, end_date), 
#                                 metrics = c("uniquePageviews", "bounces", "timeOnPage", "sessions", "newUsers", "pageviews", "exits", "sessionDuration"), 
#                                 dimensions = c("date", "landingPagePath","source", "medium", "adContent", "campaign", "region", "city"), 
#                                 dim_filters = my_filter_clause,
#                                 anti_sample = TRUE
#                                 )
# write.csv(GA_thisWk, "C:/Users/christine.iyer/Box/FY20_Advertising/FY20_GoogleAnalytics/GoogleAnalytics_CT_TravelFall18.csv", row.names = F)
# 
# GALast <- read.csv("C:/Users/christine.iyer/Box/FY20_Advertising/FY20_GoogleAnalytics/GoogleAnalytics_CT_TravelFall19.csv", header = T, stringsAsFactors = F)
# head(GALast)
# head(GA_thisWk)
# GACT <- rbind.data.frame(GALast, GA_thisWk)
# 
# write.csv(GACT, "C:/Users/christine.iyer/Box/FY20_Advertising/FY20_GoogleAnalytics/GoogleAnalytics_CT_AllTravelFall.csv", row.names = F)
# dim(GACT)
```

### Step 2
Set date parameters

```{r date range}
start_date <- "2020-02-25"
end_date <-  "2020-03-02"
```

### Step 3
Set filter for Advertising Campaigns and put it into a list format

```{r}
campaign_filter <- dim_filter(dimension="campaign",operator="REGEXP",expressions="FY20")
my_filter_clause <- filter_clause_ga4(list(campaign_filter))
```

### Step 4
Make data request

```{r request}
GA_thisWk <- google_analytics(ga_id, date_range = c(start_date, end_date), 
                                metrics = c("uniquePageviews", "bounces", "timeOnPage", "sessions", "newUsers", "pageviews", "exits", "sessionDuration"), 
                                dimensions = c("date", "landingPagePath","source", "medium", "adContent", "campaign", "region", "city"), 
                                dim_filters = my_filter_clause,
                                anti_sample = TRUE
                                )

```

### Step 5
Save the dataset

```{r}
head(GA_thisWk)
tail(GA_thisWk)
unique(GA_thisWk$source)
#GA_thisWk %>% group_by(source) %>% summarise(UPV = sum(uniquePageviews))
write.csv(GA_thisWk, "C:/Users/christine.iyer/Box/FY20_Advertising/FY20_GoogleAnalytics/GoogleAnalytics_02-25-20.csv", row.names = F)
#":\FileMaker\Uploads\GoogleAnalytics.csv"

write.csv(GA_thisWk, "file:///C:/FileMaker/Uploads/GoogleAnalytics.csv", row.names = FALSE)

```


**END HERE**


### Step 6 
Read in FY19 to date and newest dataset

```{r eval=FALSE, include=FALSE}
GoogleAnalytics <- read.csv("file:///C:/Users/christine.iyer.UAD/Box/FY19_Advertising/YearToDateDatasets/FY19_GoogleAnalytics_New.csv", header = T, stringsAsFactors = F)
GA_New_Data <- read.csv("file:///C:/Users/christine.iyer.UAD/Box/FY19_Advertising/FY19_GoogleAnalytics/GoogleAnalytics_11-06-18.csv", header = T, stringsAsFactors = F)

```

"C:\Users\christine.iyer\Downloads\report1569441670034.csv"

### Step 7
Combine new data with YTD data after making sure all the variables are compatible
```{r eval=FALSE, include=FALSE}
head(GoogleAnalytics)
head(GA_New_Data)
GoogleAnalytics$date <- as.Date(GoogleAnalytics$date, format = "%m/%d/%Y")
GA_New_Data$date <- as.Date(GA_New_Data$date, format = "%Y-%m-%d")
GA <- rbind.data.frame(GoogleAnalytics, GA_New_Data)
GA <- GA %>% mutate(adContent = toupper(adContent))
tail(GA)
```

### Step 8


Fix mislabeled Transfer Ads in GA

```{r eval=FALSE, include=FALSE}
head(GA)
GA <- GA %>% mutate(adContent = ifelse(adContent == "FY19_IG_FB_DISP_TR_UG_S_1", "FY19_IG_FB_DISP_CU_TR_S_1", 
                                ifelse(adContent == "FY19_IG_FB_DISP_TR_UG_S_2", "FY19_IG_FB_DISP_CU_TR_S_2",
                                       ifelse(adContent == "FY19_IG_FB_DISP_TR_UG_S_3", "FY19_IG_FB_DISP_CU_TR_S_3", adContent))))

unique(GA$adContent)
```


```{r eval=FALSE, include=FALSE}
write.csv(GA, "file:///C:/Users/christine.iyer.UAD/Box/FY19_Advertising/YearToDateDatasets/FY19_GoogleAnalytics_New.csv", row.names = F)
```

