---
title: "Untitled"
author: "Office of Marketing and Brand Management"
date: "2/20/2020"
output: slidy_presentation

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.width=8, 
	fig.height=2
)
```

```{r fig.height=2, fig.width=4}
library(knitr)
library(janitor)
library(tidyr)
library(zoo)
library(lubridate)
library(hms)
library(dplyr)
library(ggplot2)
library(gtable)
library(grid)
library(ggpubr)
library(kableExtra)
library(scales)
```


```{r}
# FM <- read.csv("file:///Z:/DAA/Marketing/MKT_output.csv", header = T, stringsAsFactors = F)
FM <- read.csv("C:/Users/christine.iyer/Box/AnnualCampaignVendorPerformance/MKT_output.csv", header = T, stringsAsFactors = F)
```

```{r}
FM <- FM %>% filter(Master_Adname_Type == "NC")
FM <- FM %>% mutate(Code_Audience = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1",  "TL", Code_Audience ), Code_Product = ifelse(Master_Adname == "FA20_BR_FB_VID__TL_UG_D_1",  "UG", Code_Product), Master_Results = as.numeric(Master_Results))
FM <- FM %>% select(1:8, 13, 15:19, 21:24, 26, 28:29, 31:39, 41) %>% select(Master_Date, everything())

```

```{r}
FM <- FM %>% mutate_at(10:31, ~replace(., is.na(.), 0)) %>% mutate(Master_Date = as.Date(Master_Date, format = "%Y-%m-%d")) %>% arrange(Master_Date)
colorP <- c("#F6A704", "#0E1033","#4E7B14","#A92007","#D47E0A")
FMVM <- FM %>%
  mutate(Product_Audience = paste0(Code_Product, "_", Code_Audience)) %>%
  group_by(Code_Audience,Code_Product, Code_Vendor, Code_Medium,Week = as.Date(cut(Master_Date + 1, "week")), format = "%Y-%m-%d") %>%
  summarise(
    Cost = sum(Master_Cost),
    Clicks = sum(Master_Clicks),
    Impressions = round(sum(Master_Impressions),0),
    #CTR = paste0(round(Clicks/Impressions * 100, 2), "%"),
    Bounces = sum(Master_Bounces),
    Sessions = sum(Master_Sessions),
    UPV = sum(Master_Unique_Pageviews),
    Views = sum(Master_Views),
    Completions = sum(Master_Completions),
    #BounceRate = paste0(round(Bounces/Sessions * 100, 2), "%"),
    Step1 = sum(Master_Time_On_Page)/(sum(Master_Pageviews)- sum(Master_Exits)),
    Av_TOP = round_hms(as_hms(Step1), 5),
    ClickRatePct = round(Clicks/Impressions * 100, 2),
    BounceRatePct = round(Bounces/Sessions * 100, 2),
    ViewRate = round(Views/Impressions * 100, 2),
    VTR = round(Completions/Impressions *100, 2),
    ClickableCompletions = sum(Master_Clickable_Completions),
    ClickableCompRate = round(Clicks/ClickableCompletions * 100, 2), 
    Swipes = sum(Master_Swipes), 
    SwipeUpRatePct = round(Swipes/Impressions * 100, 2),
    Opens = sum(Master_Clicks_To_Site),
    CTOR = round(Opens/Clicks * 100, 2), 
    Sends = sum(Master_Sends), 
    LIOpens = sum(Master_Opens),
    LIClicks = sum(Master_Clicks_Sponsored_InMail),
    OpenRate = round(LIOpens/Sends * 100, 2), 
    Engagements = sum(Master_Engagements),
    Results = sum(Master_Results),
    ResultsRate = round(Results/Impressions * 100, 2),
    EngagementRate = round(Engagements/Impressions * 100, 2),
    EngRate = round((sum(LIOpens)+sum(Engagements))/sum(Sends)*100, 2),  
    LICTOR = round(sum(LIClicks)/sum(LIOpens) * 100, 2)) %>%
  select(Week, Impressions, Clicks, Bounces, Sessions, Swipes, ClickRatePct, SwipeUpRatePct, UPV, BounceRatePct, Av_TOP, ClickableCompRate, VTR, CTOR,OpenRate, Sends, ViewRate, ClickableCompletions, Completions, Opens, LIOpens, LIClicks, Engagements, LICTOR, EngRate, EngagementRate, Views, Completions, Results, ResultsRate)


```





```{r Facebook Display}
FB_DISP_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = c(0.45,0.73), linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGBR <- IGD %>% 
    ggplot(aes(x = Week, y = BounceRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


FB_DISP_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_CTR = round(sum(Clicks)/sum(Impressions) * 100, 2),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_CTR = paste0(Avg_CTR, "%")))%>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r Instagram Display}
IG_DISP_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.16, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGBR <- IGD %>% 
    ggplot(aes(x = Week, y = BounceRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


IG_DISP_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_CTR = round(sum(Clicks)/sum(Impressions) * 100, 2),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_CTR = paste0(Avg_CTR, "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
 return(kable(TD))
}

```


```{r Prog Display}
DBM_DISP_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.08, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGBR <- IGD %>% 
    ggplot(aes(x = Week, y = BounceRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


DBM_DISP_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_CTR = round(sum(Clicks)/sum(Impressions) * 100, 2),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_CTR = paste0(Avg_CTR, "%")))%>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```


```{r Pinterest Display}
PIN_DISP_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.2, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGBR <- IGD %>% 
    ggplot(aes(x = Week, y = BounceRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


PIN_DISP_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_CTR = round(sum(Clicks)/sum(Impressions) * 100, 2),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_CTR = paste0(Avg_CTR, "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```


```{r Gmail Display}
GM_DISP_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = c(4, 10), linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  kable(names(FMVM))
  
  PGCTOR <- IGD %>% 
    ggplot(aes(x = Week, y = CTOR , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+
    geom_hline(yintercept = 2.48, linetype="dashed")
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGCTOR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


GM_DISP_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_CTR = paste0(round(sum(Clicks)/sum(Impressions) * 100, 2), "%"),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_CTOR = paste0(round(sum(Opens)/sum(Clicks) * 100, 2), "%"),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```


```{r LI Display}
LI_DISP_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.15, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGBR <- IGD %>% 
    ggplot(aes(x = Week, y = BounceRatePct , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGBR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


LI_DISP_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Product) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_CTR = round(sum(Clicks)/sum(Impressions) * 100, 2),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%")))%>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r LI TEXT}
LI_TEXT_PLT <- function(temp_F) {
  PGOR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 25, linetype="dashed")
  
  PGSend <- IGD %>% 
    ggplot(aes(x = Week, y = Sends , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGCTOR <- IGD %>% 
    ggplot(aes(x = Week, y = LICTOR , color = Code_Product)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+
    geom_hline(yintercept = 2.5, linetype="dashed")
  
  
  a <- ggarrange(PGSend, PGOR, PGUPV, PGCTOR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


LI_TEXT_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Product) %>%
        summarise(YTD_Sends = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_OR = round(sum(Clicks)/sum(Impressions) * 100, 2),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_CTOR = paste0(round(sum(LIClicks)/sum(Clicks) * 100, 2), "%")))%>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r Snapchat Video}
SC_VID_PLT <- function(temp_F) {
  PGSR <- IGD %>%  
    ggplot(aes(x = Week, y = SwipeUpRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.83, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGVR <- IGD %>% 
    ggplot(aes(x = Week, y = ViewRate , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  PGVTR <- IGD %>% 
    ggplot(aes(x = Week, y = VTR , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGSR, PGUPV, PGVR,PGVTR, ncol=5, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


SC_VID_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_Swipe_Rate = paste0(round(sum(Swipes)/sum(Impressions) * 100, 2), "%"),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_View_Rate = paste0(round(sum(Views)/sum(Impressions) * 100, 2), "%"),
                  Avg_VTR = paste0(round(sum(Completions)/sum(Views) * 100, 2), "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r YouTube Video}
YT_VID_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.0, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGVR <- IGD %>% 
    ggplot(aes(x = Week, y = ViewRate , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+
    geom_hline(yintercept = 20.0, linetype="dashed")
  
  PGVTR <- IGD %>% 
    ggplot(aes(x = Week, y = VTR , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    geom_hline(yintercept = 20, linetype="dashed") +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGVR,PGVTR, ncol=5, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


YT_VID_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  ClickRatePct = paste0(round(sum(Clicks)/sum(Impressions) * 100, 2), "%"),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_View_Rate = paste0(round(sum(Views)/sum(Impressions) * 100, 2), "%"),
                  Avg_VTR = paste0(round(sum(Completions)/sum(Views) * 100, 2), "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r Facebook Video}
FB_VID_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.0, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGVR <- IGD %>% 
    ggplot(aes(x = Week, y = ViewRate , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+
    geom_hline(yintercept = 20.0, linetype="dashed")
  
  PGVTR <- IGD %>% 
    ggplot(aes(x = Week, y = VTR , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    geom_hline(yintercept = 20, linetype="dashed") +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGVR,PGVTR, ncol=5, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


FB_VID_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  ClickRatePct = paste0(round(sum(Clicks)/sum(Impressions) * 100, 2), "%"),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_View_Rate = paste0(round(sum(Views)/sum(Impressions) * 100, 2), "%"),
                  Avg_VTR = paste0(round(sum(Completions)/sum(Views) * 100, 2), "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r Instagram Video}
IG_VID_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.0, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGVR <- IGD %>% 
    ggplot(aes(x = Week, y = ViewRate , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+
    geom_hline(yintercept = 20.0, linetype="dashed")
  
  PGVTR <- IGD %>% 
    ggplot(aes(x = Week, y = VTR , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    geom_hline(yintercept = 20, linetype="dashed") +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGVR,PGVTR, ncol=5, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


IG_VID_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  ClickRatePct = paste0(round(sum(Clicks)/sum(Impressions) * 100, 2), "%"),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_View_Rate = paste0(round(sum(Views)/sum(Impressions) * 100, 2), "%"),
                  Avg_VTR = paste0(round(sum(Completions)/sum(Views) * 100, 2), "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r Programmatic Video}
DBM_VID_PLT <- function(temp_F) {
  PGCTR <- IGD %>%  
    ggplot(aes(x = Week, y = ClickRatePct , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.0, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGVR <- IGD %>% 
    ggplot(aes(x = Week, y = ViewRate , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+
    geom_hline(yintercept = 20.0, linetype="dashed")
  
  PGVTR <- IGD %>% 
    ggplot(aes(x = Week, y = VTR , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    geom_hline(yintercept = 20, linetype="dashed") +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  a <- ggarrange(PGImp, PGCTR, PGUPV, PGVR,PGVTR, ncol=5, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


DBM_VID_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  ClickRatePct = paste0(round(sum(Clicks)/sum(Impressions) * 100, 2), "%"),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_BR = paste0(round(sum(Bounces)/sum(Sessions) * 100, 2), "%"),
                  Avg_View_Rate = paste0(round(sum(Views)/sum(Impressions) * 100, 2), "%"),
                  Avg_VTR = paste0(round(sum(Completions)/sum(Views) * 100, 2), "%"))) %>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```

```{r Twitter Display}
TW_DISP_PLT <- function(temp_F) {
  PGER <- IGD %>%  
    ggplot(aes(x = Week, y = EngagementRate , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank()) +
    geom_hline(yintercept = 0.079, linetype="dashed")
  
  PGImp <- IGD %>% 
    ggplot(aes(x = Week, y = Impressions , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black")) +
    theme(axis.title.x=element_blank(),
          axis.ticks.x=element_blank()) 
  
  
  PGUPV <- IGD %>% 
    ggplot(aes(x = Week, y = UPV , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
          panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())
  
  
  
  PGRR <- IGD %>% 
    ggplot(aes(x = Week, y = ResultsRate , color = Code_Audience)) +
    geom_line(size = 1.2) +
    scale_color_manual(values = colorP) +
    theme_bw() + 
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.title.x=element_blank(),panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"),axis.ticks.x=element_blank())+
    geom_hline(yintercept = 1.11, linetype="dashed")
  
  
  a <- ggarrange(PGImp, PGER, PGUPV, PGRR, ncol=4, nrow=1, common.legend = TRUE, legend="right")
  annotate_figure(a, text_grob(paste0( IGD$Code_Vendor, "_ ", IGD$Code_Medium, "_ ", IGD$Code_Product), color = "darkblue", face = "plain", size = 18, just = "right"))
  
  
  
}


TW_DISP_TBL <- function(temp_C){
  TD <- kable(IGD %>%
  group_by(Code_Audience) %>%
        summarise(YTD_Impressions = prettyNum(round(sum(Impressions),0), big.mark = ","),
                  Avg_ER = round(sum(Engagements)/sum(Impressions) * 100, 2),
                  YTD_UPV = prettyNum(round(sum(UPV),0), big.mark = ","),
                  Avg_RR = paste0(round(sum(Results)/sum(Impressions) * 100, 2), "%")))%>%
kable_styling("striped", full_width = F) %>%
  row_spec(0, angle = -30, font_size = 13)
 return(TD)
}

```
## FB_DISP_UG {.tabset .tabset-fade}

### Seven Day

```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+20
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" & Code_Medium == "DISP" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 




FB_DISP_PLT(a)
FB_DISP_TBL(TD)

```

### Sixty Day


```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+60
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" & Code_Medium == "DISP" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 




FB_DISP_PLT(a)
FB_DISP_TBL(TD)

```

### Year to Date

```{r}

start_Date <- as.Date("2019-08-15")
#end_Date <- max(FMVMWeek)
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" & Code_Medium == "DISP" & Code_Audience == "HS" & Week >= start_Date & Week <= max(Week)) 




FB_DISP_PLT(a)
FB_DISP_TBL(TD)

```

## IG_DISP_UG{.tabset .tabset-fade}

### Seven Day

```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date + 20
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" & Code_Medium == "DISP" & Code_Product == "UG" & Week >= start_Date & Week <= end_Date)
IG_DISP_PLT(a)
IG_DISP_TBL(TD)
```

### Sixty Day

```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date + 60
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" & Code_Medium == "DISP" & Code_Product == "UG" & Week >= start_Date & Week <= end_Date)
IG_DISP_PLT(a)
IG_DISP_TBL(TD)
```

### Year to Date

```{r}
start_Date <- as.Date("2019-08-15")

IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" & Code_Medium == "DISP" & Code_Product == "UG" & Week >= start_Date & Week <= max(Week))
IG_DISP_PLT(a)
IG_DISP_TBL(TD)
```

## DBM_DISP_UG{.tabset .tabset-fade}

### Seven Day

```{r}
start_Date <- as.Date("2019-08-01")
end_Date <- as.Date("2019-09-17")
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" & Code_Medium == "DISP" & Code_Product == "UG"& Week >= start_Date & Week <= end_Date) 




DBM_DISP_PLT(a)
DBM_DISP_TBL(TD)
```

### Sixty Day

```{r}
start_Date <- as.Date("2019-08-01")
end_Date <- start_Date + 60
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" & Code_Medium == "DISP" & Code_Product == "UG"& Week >= start_Date & Week <= end_Date) 




DBM_DISP_PLT(a)
DBM_DISP_TBL(TD)
```

### Year to Date

```{r}
start_Date <- as.Date("2019-08-01")
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" & Code_Medium == "DISP" & Code_Product == "UG"& Week >= start_Date & Week <= max(Week)) 




DBM_DISP_PLT(a)
DBM_DISP_TBL(TD)
```

## PIN_DISP_UG{.tabset .tabset-fade}

### Seven Day Report

```{r}
start_Date <- as.Date("2019-09-01")
end_Date <- start_Date +20
IGD <- FMVM %>% 
  filter(Code_Vendor == "PIN" & Code_Medium == "DISP" & Code_Product == "UG" & Week >= start_Date & Week <= end_Date) 
PIN_DISP_PLT(a)
PIN_DISP_TBL(TD)
```

### Sixty Day Report

```{r}
start_Date <- as.Date("2019-09-01")
end_Date <- start_Date +60
IGD <- FMVM %>% 
  filter(Code_Vendor == "PIN" & Code_Medium == "DISP" & Code_Product == "UG" & Week >= start_Date & Week <= end_Date) 
PIN_DISP_PLT(a)
PIN_DISP_TBL(TD)
```

### Year to Date 

```{r}
start_Date <- as.Date("2019-09-01")
IGD <- FMVM %>% 
  filter(Code_Vendor == "PIN" & Code_Medium == "DISP" & Code_Product == "UG" & Week >= start_Date & Week <= max(Week)) 
PIN_DISP_PLT(a)
PIN_DISP_TBL(TD)
```

## GM_TEXT{.tabset .tabset-fade}

### Seven Day Report

```{r}
start_Date <- as.Date("2019-08-01")
end_Date <- start_Date +20
IGD <- FMVM %>% 
  filter(Code_Vendor == "GM"  & Week >= start_Date & Week <= end_Date) 



           
GM_DISP_PLT(a)
GM_DISP_TBL(TD)

```

### Sixty Day

```{r}
start_Date <- as.Date("2019-08-01")
end_Date <- start_Date +60
IGD <- FMVM %>% 
  filter(Code_Vendor == "GM"  & Week >= start_Date & Week <= end_Date) 
GM_DISP_PLT(a)
GM_DISP_TBL(TD)
```


### Year to Date

```{r}
start_Date <- as.Date("2019-08-01")
IGD <- FMVM %>% 
  filter(Code_Vendor == "GM"  & Week >= start_Date & Week <= max(Week)) 
GM_DISP_PLT(a)
GM_DISP_TBL(TD)

```



## LI_DISP{.tabset .tabset-fade}

### Seven Day Report

```{r}
start_Date <- as.Date("2019-08-01")
end_Date <- start_Date + 20
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" & Code_Medium == "DISP"  & Week >= start_Date & Week <= end_Date) 
LI_DISP_PLT(a)
LI_DISP_TBL(TD)
```

### Sixty Day Report

```{r}
start_Date <- as.Date("2019-08-01")
end_Date <- start_Date + 60
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" & Code_Medium == "DISP"  & Week >= start_Date & Week <= end_Date) 
LI_DISP_PLT(a)
LI_DISP_TBL(TD)
```

### Year to Date

```{r}
start_Date <- as.Date("2019-08-01")
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" & Code_Medium == "DISP"  & Week >= start_Date & Week <= max(Week)) 
LI_DISP_PLT(a)
LI_DISP_TBL(TD)
```


## LI_TEXT{.tabset .tabset-fade}

### Phase 1

```{r}
start_Date <- as.Date("2019-08-04")
end_Date <- start_Date + 30
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" & Code_Medium == "TEXT"  & Week >= start_Date & Week <= end_Date & Code_Product != "DC") 
LI_TEXT_PLT(a)
LI_TEXT_TBL(TD)

```

### Phase 2

```{r}
start_Date <- as.Date("2019-09-27")
end_Date <- start_Date + 80
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" & Code_Medium == "TEXT"  & Week >= start_Date & Week <= end_Date) 
LI_TEXT_PLT(a)
LI_TEXT_TBL(TD)

```

### Year to Date

```{r}
start_Date <- as.Date("2019-08-27")
IGD <- FMVM %>% 
  filter(Code_Vendor == "LI" & Code_Medium == "TEXT"  & Week >= start_Date & Week <= max(Week)) 
LI_TEXT_PLT(a)
LI_TEXT_TBL(TD)

```


## SC_VID

### Seven Day Report

```{r}
start_Date <- as.Date("2019-10-29")
end_Date <- start_Date + 20
IGD <- FMVM %>% 
  filter(Code_Vendor == "SC" & Code_Medium == "VID"  & Week >= start_Date & Week <= end_Date) 
SC_VID_PLT(a)
SC_VID_TBL(TD)
```

### Sixty Day Report

```{r}
start_Date <- as.Date("2019-10-29")
end_Date <- start_Date + 60
IGD <- FMVM %>% 
  filter(Code_Vendor == "SC" & Code_Medium == "VID"  & Week >= start_Date & Week <= end_Date) 
SC_VID_PLT(a)
SC_VID_TBL(TD)
```

### Year to Date

```{r}
start_Date <- as.Date("2019-10-29")
IGD <- FMVM %>% 
  filter(Code_Vendor == "SC" & Code_Medium == "VID"  & Week >= start_Date & Week <= max(Week)) 
SC_VID_PLT(a)
SC_VID_TBL(TD)
```


## YouTube

### Seven Day Report

```{r}
start_Date <- as.Date("2019-10-29")
end_Date <- start_Date + 20
IGD <- FMVM %>% 
  filter(Code_Vendor == "YT" & Code_Medium == "VID"  & Week >= start_Date & Week <= end_Date) 
YT_VID_PLT(a)
YT_VID_TBL(TD)
```

### Sixty Day Report

```{r}
start_Date <- as.Date("2019-10-29")
end_Date <- start_Date + 60
IGD <- FMVM %>% 
  filter(Code_Vendor == "YT" & Code_Medium == "VID"  & Week >= start_Date & Week <= end_Date) 
YT_VID_PLT(a)
YT_VID_TBL(TD)
```

### Year to Date

```{r}
start_Date <- as.Date("2019-10-29")
IGD <- FMVM %>% 
  filter(Code_Vendor == "YT" & Code_Medium == "VID"  & Week >= start_Date & Week <= max(Week)) 
YT_VID_PLT(a)
YT_VID_TBL(TD)
```

## FB_VID_HS

### Seven Day

```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+20
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 




FB_VID_PLT(a)
FB_VID_TBL(TD)

```

### Sixty Day


```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+60
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 




FB_VID_PLT(a)
FB_VID_TBL(TD)

```

### Year to Date

```{r}

start_Date <- as.Date("2019-08-15")
#end_Date <- max(FMVMWeek)
IGD <- FMVM %>% 
  filter(Code_Vendor == "FB" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= max(Week)) 




FB_VID_PLT(a)
FB_VID_TBL(TD)

```

## IG_VID_UG

### Seven Day

```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+20
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 




IG_VID_PLT(a)
IG_VID_TBL(TD)

```

### Sixty Day


```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+60
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 
IG_VID_PLT(a)
IG_VID_TBL(TD)

```

### Year to Date

```{r}

start_Date <- as.Date("2019-08-15")
#end_Date <- max(FMVMWeek)
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= max(Week)) 
IG_VID_PLT(a)
IG_VID_TBL(TD)

```

## DBM_VID_UG

### Seven Day

```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+20
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 
DBM_VID_PLT(a)
DBM_VID_TBL(TD)
```

### Sixty Day


```{r}
start_Date <- as.Date("2019-08-15")
end_Date <- start_Date+60
IGD <- FMVM %>% 
  filter(Code_Vendor == "IG" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= end_Date) 
DBM_VID_PLT(a)
DBM_VID_TBL(TD)
```

### Year to Date

```{r}

start_Date <- as.Date("2019-08-15")
#end_Date <- max(FMVMWeek)
IGD <- FMVM %>% 
  filter(Code_Vendor == "DBM" & Code_Medium == "VID" & Code_Audience == "HS" & Week >= start_Date & Week <= max(Week)) 
DBM_VID_PLT(a)
DBM_VID_TBL(TD)
```



## TW_DISP_UG

### Seven Day Report

```{r}
start_Date <- as.Date("2019-10-29")
end_Date <- start_Date + 20
IGD <- FMVM %>% 
  filter(Code_Vendor == "TW" & Code_Medium == "DISP"  & Week >= start_Date & Week <= end_Date) 
TW_DISP_PLT(a)
TW_DISP_TBL(TD)
```

### Sixty Day Report

```{r}
start_Date <- as.Date("2019-10-29")
end_Date <- start_Date + 60
IGD <- FMVM %>% 
  filter(Code_Vendor == "TW" & Code_Medium == "DISP"  & Week >= start_Date & Week <= end_Date) 
TW_DISP_PLT(a)
TW_DISP_TBL(TD)
```

### Year to Date

```{r}
start_Date <- as.Date("2019-10-29")
IGD <- FMVM %>% 
  filter(Code_Vendor == "TW" & Code_Medium == "DISP"  & Week >= start_Date & Week <= max(Week)) 
TW_DISP_PLT(a)
TW_DISP_TBL(TD)
```
